Effects of the body force on the evacuation dynamics

### 2019-12-26 paper.tex
Update paper.tex

No body contacts were reported in Refs.~\cite{seyfried_2007,weidmann_1992} 
since these experiments correspond to the low density regime. At this instance, 
the pedestrian does not feel to be too close to the others....    \\

>>>>

The reported data from Ref.~\cite{song_2019} correspond to the crowded 
environment of the Beijing subway. This environment was not suitable for 
providing information on the step distance $B$, but estimates for the 
desired speed and the body compresibility could be achieved. The reported 
magnitude $k$ assesses either the clothes and the body compressibility. The 
final value, though, is linearly related to the compression $x$. \\

We measured the maximum forces attainable at the subway in Buenos Aires, 
Argentina. Our preliminary results show that pedestrians feel uncomfortable 
whenever a body force ranging from $5$ to $20\,$N is applied for at least ten 
minutes. Short lasting forces (say, less than 4 minutes) may also be perceived 
as uncomfortable for values ranging from $10$ to $30\,$N. We also recorded body 
forces up to $60\,$N during very short ``hits''. The comparison with the 
fittings provided by Ref.~\cite{song_2019} shows that these magnitudes 
accomplish densities around 5 people/m$^2$.     \\

The maximum (realistic) compressions may be computed from the relation 
$F=k(x)\,x$ and the compressibility $k(x)$ reported in Table~\ref{table_data}. 
An ``uncomfortable'' body force of $30\,$N can address compressions in the 
range of $0.030-0.055\,$m. Also, a ``hitting'' force of $60\,$N can address 
compressions between $0.045$ and $0.065\,$m. Thus, according to 
Table~\ref{table_data}, we may expect experimental values for $k(x)$ up to 
$1000\,$kg/s$^2$ (for $30\,$N), or, up to $1400\,$kg/s$^2$ (for $60\,$N). \\

Besides, no realiable values for the sliding friction $\kappa$ appears to be 
available in the literature (to our knowledge). We may pressume, however, that 
the sliding friction approaches a fraction of the body force. We will come back 
to this issue in Section~\ref{background}. \\
